Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-11-28 Docs/IJES/journal.tex
updating file structure

%\JOURNALNAME{\TEN{\it Int. J. System Control and Information
%Processing,
%Vol. \theVOL, No. \theISSUE, \thePUBYEAR\hfill\thepage}}%
%
%\def\BottomCatch{%
%\vskip -10pt
%\thispagestyle{empty}%
%\begin{table}[b]%
%\NINE\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcr@{}}%
%\\[-12pt]
%Copyright \copyright\ 2012 Inderscience Enterprises Ltd. & &%
%\end{tabular*}%
%\vskip -30pt%
%%%\vskip -35pt%
%\end{table}%
%}
\makeatother

@@

\vspace{-2 mm}
\begin{align}
\label{hardware-costs}
H_p  &= \Sigma_{V_i \in V_h} h_i,
\end{align}

@@

In the ESBMC algorithm, which is shown below, it is not necessary to add slack variables, because the modulus operation is kept, which reduces the number of variables to be solved.

@@

\bibitem[\protect\citeauthoryear{Mann et al.}{2007}]{Mann2007}
Mann, A., Orban, A. and Arato, P. (2007) 'Finding optimal hardware/software partitions', {\it Formal Methods in System Design}, Vol. 31, No. 3, pp.241--263

@@

\bibitem[\protect\citeauthoryear{Trindade et al.}{2016}]{Trindade2016}
Trindade, A., Ismail, H. and Cordeiro, L. (2016) 'Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems (short paper)', {\it V Brazilian Symp. on Computing Systems Engineering (to appear)}

\bibitem[\protect\citeauthoryear{Bjorner et al.}{2015}]{Bjorner2015}
Bjorner, N., Phan, A. and Fleckenstein, L. (2015) 'vZ - An Optimizing SMT Solver', {\it Proc. of the Intl. Conf. on Tools and Algorithms for the Construction and Analysis of Systems}, Vol. 9035, pp.194--199

\bibitem[\protect\citeauthoryear{Tang et al.}{2010}]{Tang2009}
Tang, T., Lin, Y. and Ren, X. (2010) 'Mapping OpenMP concepts to the stream programming model', {\it Proc. of the Intl. Conf. on Computer Science Education}, pp.1900--1905

@@

\bibitem[\protect\citeauthoryear{Cordeiro et al.}{2012}]{Cordeiro2012}
Cordeiro, L. Fischer, B. and Marques-Silva, J. (2012) 'SMT-based Bounded Model Checking for Embedded ANSI-C Software', {\it IEEE Transactions on Software Engineering}, Vol. 38, No. 4, pp.957--974

@@

\bibitem[\protect\citeauthoryear{Biere et al.}{2009}]{Biere2009}
Biere, A., Heule, M., Maaren, H. and Walsh, T. {2009} 'Bounded Model Checking', {\it Handbook of Satisfiability}

\bibitem[\protect\citeauthoryear{Clarke et al.}{2001}]{Clarke2001}
Clarke, E., Biere, A., Raimi, R. and Zhu, Y. (2001) 'Bounded model checking using satisfiability solving', {\it Formal Methods in System Design}, Vol. 19, No. 1, pp.7--34

\bibitem[\protect\citeauthoryear{Armando et al.}{2009}]{Armando2009}
Armando, A., Mantovani, J. and Platania, L. (2009) 'Bounded model checking of software using SMT solvers instead of SAT solvers', {\it Intl. Journal on Software Tools for Technology Transfer}, Vol. 11, No. 1, pp.69--83

@@

\bibitem[\protect\citeauthoryear{Ramalho et al.}{2013}]{Ramalho2013}
Ramalho, M., Freitas, M., Sousa, F., Marques, H., Cordeiro, L. and Fischer, B. (2013) 'SMT-Based Bounded Model Checking of C++ Programs', {\it Intl. Conf. and Workshops on the Engineering of Computer-Based Systems}, pp.147--156

@@

\bibitem[\protect\citeauthoryear{Barrett et al.}{2011}]{Barrett2011}
Barrett, C., Conway, C., Deters, M., Hadarean, L., Jovanovic, D., King, T., Reynolds, A. and Tinelli, C. (2011) 'CVC4', {\it Proc. of the Intl. Conf. on Computer-Aided Verification}, Vol. 6806, pp.171--177

\bibitem[\protect\citeauthoryear{Bozzano et al.}{2005}]{Bozzano2005}
Bozzano, M., Bruttomesso, R., Cimatti, A., Junttila, T., Rossum, P., Schulz, S. and Sebastiani, R. (2005) 'MathSAT: Tight integration of SAT and mathematical decision procedures', {\it Journal of Automated Reasoning}, Vol. 35, No. 1-3, pp.265--293

@@

\bibitem[\protect\citeauthoryear{Wu et al.}{2014}]{Wu2014}
Wu M., Wu, W., Tai, N., Zhao, H., Fan, J. and Yuan, N. (2014) 'Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP', {\it Proc. of the Intl. Conf. on Software Engineering and Service Science}, pp.921--924

@@

\bibitem[\protect\citeauthoryear{Cormen et al.}{2009}]{Cormem}
Cormen, T., Leiserson, C., Rivest, R. and Stein, C. (2009) 'Introduction to Algorithms', {\it MIT Press}, Vol. I-XIX, pp.1--1292

@@

\bibitem[\protect\citeauthoryear{Guthaus et al.}{2011}]{Guthaus2001}
Guthaus, M., Ringenberg, J., Ernst, D., Austin, T., Mudge, T. and Brown, R. (2011) 'MiBench: A free, commercially representative embedded benchmark suite', {\it Proc. of the annual workshop on workload characterization}, pp.3--14

\bibitem[\protect\citeauthoryear{Arato et al.}{2005}]{Arato2005}
Arato, P., Mann, A., Orban, A. (2005) 'Algorithmic aspects of hardware/software partitioning', {\it ACM Transactions on Design Automation of Electronic Systems}, Vol. 1, No. 1, pp.136--156

\bibitem[\protect\citeauthoryear{Holzmann et al.}{2011}]{Holzmann2011}
Holzmann, G., Joshi, R. and Groce, A. (2011) 'Swarm Verification Techniques', {\it IEEE Transactions on Software Engineering}, Vol. 37, No. 6, pp.845--857

\bibitem[\protect\citeauthoryear{Wintersteiger et al.}{2009}]{Wintersteiger2009}
Wintersteiger, C., Hamadi, Y. and Moura, L. (2009) 'A Concurrent Portfolio Approach to SMT Solving', {\it Proc. of the Intl. Conf. on Computer-Aided Verification}, Vol. 5643, pp.715--720

\bibitem[\protect\citeauthoryear{Qawasmeh et al.}{2014}]{Qawasmeh2014}
Qawasmeh, A., Malik, A. and Chapman, B. (2014) 'OpenMP task scheduling analysis via OpenMP runtime API and tool visualization', {\it Proc. of the Intl. Symp. on Parallel Distributed processing}, pp.1049--1058

\bibitem[\protect\citeauthoryear{Pavlinovi et al.}{2015}]{Pavlinovic2015}
Pavlinovi, Z., King, T. and Wies, T. (2015) 'Practical SMT-Based Type Error Localization', {\it Proc. of the Intl. Conf. on Functional Programming}, pp.412--423

@@

\bibitem[\protect\citeauthoryear{Holzmann et al.}{2011}]{Holzmann11}
Holzmann, G., Joshi, R. and Groce, A. (2011) 'Swarm Verification Techniques', {\it IEEE Transactions Software Engineering}, Vol. 9206, pp.845--857

 \end{thebibliography}
\end{document}

>>>>

\JOURNALNAME{\TEN{\it International Journal of Embedded Systems,
Vol. \theVOL, No. \theISSUE, \thePUBYEAR\hfill\thepage}
}

%
%
%\def\BottomCatch{%
%\vskip -10pt
%\thispagestyle{empty}%
%\begin{table}[b]%
%\NINE\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcr@{}}%
%\\[-12pt]
%Copyright \copyright\ 2012 Inderscience Enterprises Ltd. & &%
%\end{tabular*}%
%\vskip -30pt%
%%%\vskip -35pt%
%\end{table}%
%}

\makeatother

@@

\vspace{-5 mm}
\begin{align}
\label{hardware-costs}
H_p  &= \Sigma_{V_i \in V_h} h_i,
\end{align}

@@

In the ESBMC algorithm is not necessary to add slack variables, because the modulus operation is kept, which reduces the number of variables to be solved.

@@

\bibitem[\protect\citeauthoryear{Mann \textit{et al.}}{2007}]{Mann2007}
Mann, A., Orban, A. and Arato, P. (2007) 'Finding optimal hardware/software partitions', {\it Formal Methods in System Design}, Vol. 31, No. 3, pp.241--263

@@

\bibitem[\protect\citeauthoryear{Trindade \textit{et al.}}{2016}]{Trindade2016}
Trindade, A., Ismail, H. and Cordeiro, L. (2016) 'Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems (short paper)', {\it V Brazilian Symp. on Computing Systems Engineering (to appear)}

\bibitem[\protect\citeauthoryear{Bjorner \textit{et al.}}{2015}]{Bjorner2015}
Bjorner, N., Phan, A. and Fleckenstein, L. (2015) 'vZ - An Optimizing SMT Solver', {\it Proc. of the Intl. Conf. on Tools and Algorithms for the Construction and Analysis of Systems}, Vol. 9035, pp.194--199

\bibitem[\protect\citeauthoryear{Tang \textit{et al.}}{2010}]{Tang2009}
Tang, T., Lin, Y. and Ren, X. (2010) 'Mapping OpenMP concepts to the stream programming model', {\it Proc. of the Intl. Conf. on Computer Science Education}, pp.1900--1905

@@

\bibitem[\protect\citeauthoryear{Cordeiro \textit{et al.}}{2012}]{Cordeiro2012}
Cordeiro, L. Fischer, B. and Marques-Silva, J. (2012) 'SMT-based Bounded Model Checking for Embedded ANSI-C Software', {\it IEEE Transactions on Software Engineering}, Vol. 38, No. 4, pp.957--974

@@

\bibitem[\protect\citeauthoryear{Biere \textit{et al.}}{2009}]{Biere2009}
Biere, A., Heule, M., Maaren, H. and Walsh, T. {2009} 'Bounded Model Checking', {\it Handbook of Satisfiability}

\bibitem[\protect\citeauthoryear{Clarke \textit{et al.}}{2001}]{Clarke2001}
Clarke, E., Biere, A., Raimi, R. and Zhu, Y. (2001) 'Bounded model checking using satisfiability solving', {\it Formal Methods in System Design}, Vol. 19, No. 1, pp.7--34

\bibitem[\protect\citeauthoryear{Armando \textit{et al.}}{2009}]{Armando2009}
Armando, A., Mantovani, J. and Platania, L. (2009) 'Bounded model checking of software using SMT solvers instead of SAT solvers', {\it Intl. Journal on Software Tools for Technology Transfer}, Vol. 11, No. 1, pp.69--83

@@

\bibitem[\protect\citeauthoryear{Ramalho \textit{et al.}}{2013}]{Ramalho2013}
Ramalho, M., Freitas, M., Sousa, F., Marques, H., Cordeiro, L. and Fischer, B. (2013) 'SMT-Based Bounded Model Checking of C++ Programs', {\it Intl. Conf. and Workshops on the Engineering of Computer-Based Systems}, pp.147--156

@@

\bibitem[\protect\citeauthoryear{Barrett \textit{et al.}}{2011}]{Barrett2011}
Barrett, C., Conway, C., Deters, M., Hadarean, L., Jovanovic, D., King, T., Reynolds, A. and Tinelli, C. (2011) 'CVC4', {\it Proc. of the Intl. Conf. on Computer-Aided Verification}, Vol. 6806, pp.171--177

\bibitem[\protect\citeauthoryear{Bozzano \textit{et al.}}{2005}]{Bozzano2005}
Bozzano, M., Bruttomesso, R., Cimatti, A., Junttila, T., Rossum, P., Schulz, S. and Sebastiani, R. (2005) 'MathSAT: Tight integration of SAT and mathematical decision procedures', {\it Journal of Automated Reasoning}, Vol. 35, No. 1-3, pp.265--293

@@

\bibitem[\protect\citeauthoryear{Wu \textit{et al.}}{2014}]{Wu2014}
Wu M., Wu, W., Tai, N., Zhao, H., Fan, J. and Yuan, N. (2014) 'Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP', {\it Proc. of the Intl. Conf. on Software Engineering and Service Science}, pp.921--924

@@

\bibitem[\protect\citeauthoryear{Cormen \textit{et al.}}{2009}]{Cormem}
Cormen, T., Leiserson, C., Rivest, R. and Stein, C. (2009) 'Introduction to Algorithms', {\it MIT Press}, Vol. I-XIX, pp.1--1292

@@

\bibitem[\protect\citeauthoryear{Guthaus \textit{et al.}}{2011}]{Guthaus2001}
Guthaus, M., Ringenberg, J., Ernst, D., Austin, T., Mudge, T. and Brown, R. (2011) 'MiBench: A free, commercially representative embedded benchmark suite', {\it Proc. of the annual workshop on workload characterization}, pp.3--14

\bibitem[\protect\citeauthoryear{Arato \textit{et al.}}{2005}]{Arato2005}
Arato, P., Mann, A., Orban, A. (2005) 'Algorithmic aspects of hardware/software partitioning', {\it ACM Transactions on Design Automation of Electronic Systems}, Vol. 1, No. 1, pp.136--156

\bibitem[\protect\citeauthoryear{Holzmann \textit{et al.}}{2011}]{Holzmann2011}
Holzmann, G., Joshi, R. and Groce, A. (2011) 'Swarm Verification Techniques', {\it IEEE Transactions on Software Engineering}, Vol. 37, No. 6, pp.845--857

\bibitem[\protect\citeauthoryear{Wintersteiger \textit{et al.}}{2009}]{Wintersteiger2009}
Wintersteiger, C., Hamadi, Y. and Moura, L. (2009) 'A Concurrent Portfolio Approach to SMT Solving', {\it Proc. of the Intl. Conf. on Computer-Aided Verification}, Vol. 5643, pp.715--720

\bibitem[\protect\citeauthoryear{Qawasmeh \textit{et al.}}{2014}]{Qawasmeh2014}
Qawasmeh, A., Malik, A. and Chapman, B. (2014) 'OpenMP task scheduling analysis via OpenMP runtime API and tool visualization', {\it Proc. of the Intl. Symp. on Parallel Distributed processing}, pp.1049--1058

\bibitem[\protect\citeauthoryear{Pavlinovi \textit{et al.}}{2015}]{Pavlinovic2015}
Pavlinovi, Z., King, T. and Wies, T. (2015) 'Practical SMT-Based Type Error Localization', {\it Proc. of the Intl. Conf. on Functional Programming}, pp.412--423

@@

\bibitem[\protect\citeauthoryear{Holzmann \textit{et al.}}{2011}]{Holzmann11}
Holzmann, G., Joshi, R. and Groce, A. (2011) 'Swarm Verification Techniques', {\it IEEE Transactions Software Engineering}, Vol. 9206, pp.845--857

\end{thebibliography}

\end{document}
